Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-21 latex/article.tex
wip
hop

The general idea is to perform and Integral Invariant computation on
GPU at each vertex of the generated triangular mesh. First note that
of the LoD criterion is removed, each MC vertex is exactly centered at
a surfel center. At different depth of the octree, MC vertices still
correspond to surfel centers of subsampled versions of the input
object. Hence, Integral Invariant framework defined in
Section~\ref{sec:curv-tens-estim} is consistent with the triangular
surface obtained on GPU: triangles are used for visualization purposes
but all computations are performed on the digital object $Z$ and thus
estimators
(\ref{eq:dig-curvature-estimator-k}),
(\ref{eq:dig-curvature-estimator-H}), (\ref{eq:dig-curvature-estimator-k1})
and (\ref{eq:dig-curvature-estimator-k2}).

To implement the integration on $B_R(\vx)\cap\Shape$\todo{fix Z vs X}
(Fig.~\ref{fig:approx}-$a$), a naive approach consists in scanning all
digital points inside such domain (Fig.~\ref{fig:approx}-$b$) and then
to estimate the geometrical moment as the sum of the geometrical
moments of each elementary cubes lying in the intersection. On GPU,
\emph{mipmap} textures to obtain a multiresolution information: if the
input binary object is stored in a 3D texture, GPU hardware can
construct a multiresolution pyramid such that 8 neighboring voxel
intensities at level $l$ are averaged to define the voxel value at
level $l+1$. If the level 0 corresponds to the binary input object, at
a given level $l$, a voxel $(x,y,z)$ contains the fraction of $Z$
belonging to the cube of center $(x,y,z)$ and edge length $2^l$. As a
consequence, we can approximate the volume of $B_R(x)\cap\Shape$ by
considering mipmap values at a given resolution $l$
(Fig.~\ref{fig:approx}-$c$). In this case, errors only occurs for
cells lying inside $\Shape$ (with density 1) not entirely covered by
$B_R(\vx)$.
\begin{figure}
  \begin{center}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx1}}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx-reg-1}}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx-reg-2}}
  \end{center}
  \caption{Integral computation with an area estimation from pixel
    counting $(b)$ or from densities (represented by different
    grayvalues) in a mipmap approximation of $\Shape$.}
  \label{fig:approx}
\end{figure}

@@

\subsection{Realtime computation on GPU}

>>>>

The general idea is to perform and Integral Invariant computation on
GPU at each vertex of the generated triangular mesh. First note that
of the LoD criterion is removed, each MC vertex is exactly centered at
a surfel center. At different depth of the octree, MC vertices still
correspond to surfel centers of subsampled versions of the input
object. Hence, Integral Invariant framework defined in
Section~\ref{sec:curv-tens-estim} is consistent with the triangular
surface obtained on GPU: triangles are used for visualization purposes
but all computations are performed on the digital object $\DSh$ and thus
estimators
(\ref{eq:dig-curvature-estimator-k}),
(\ref{eq:dig-curvature-estimator-H}), (\ref{eq:dig-curvature-estimator-k1})
and (\ref{eq:dig-curvature-estimator-k2}).

To implement the integration on $B_R(\vx)\cap\Shape$\todo{Check ball
  radii w.r.t. notations in sect2)
(Fig.~\ref{fig:approx}-$a$), a naive approach consists in scanning all
digital points inside such domain (Fig.~\ref{fig:approx}-$b$) and then
to estimate the geometrical moment as the sum of the geometrical
moments of each elementary cubes lying in the intersection. On GPU,
\emph{mipmap} textures to obtain a multiresolution information: if the
input binary object is stored in a 3D texture, GPU hardware can
construct a multiresolution pyramid such that 8 neighboring voxel
intensities at level $l$ are averaged to define the voxel value at
level $l+1$. If the level 0 corresponds to the binary input object, at
a given level $l$, a voxel $(x,y,z)$ contains the fraction of $\DSh$
belonging to the cube of center $(x,y,z)$ and edge length $2^l$. As a
consequence, we can approximate the volume of $B_R(x)\cap\Shape$ by
considering mipmap values at a given resolution $l$
(Fig.~\ref{fig:approx}-$c$). In this case, errors only occurs for
cells lying inside $\Shape$ (with density 1) not entirely covered by
$B_R(\vx)$.
\begin{figure}
  \begin{center}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx1}}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx-reg-1}}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx-reg-2}}
  \end{center}
  \caption{Integral computation with an area estimation from pixel
    counting $(b)$ or from densities (represented by different
    grayvalues) in a mipmap approximation of $\Shape$.}
  \label{fig:approx}
\end{figure}

@@

\subsection{Realtime computation on GPU}
\begin{itemize}
\item   Variante 1 : hierarchique avec précalcul cells
\item   Variante 2 : reg avec autoraffinement
\end{itemize}
